Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-30 paper/lostanlenRelevanceScattering.tex
improve description of Eq 6

The similarity between the scene centroids $\mu_m^u$ over the entire dataset, is computed using a radial basis function (RBF) kernel $K$ combined with a local scaling method~\cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{mn}^{uv} = \exp\left( - \dfrac{\Vert \mu_m^u - \mu_n^v \Vert^2}{\Vert \mu_m^u - \mu_{m,q}^u \Vert \Vert \mu_n^v - \mu_{n,q}^v \Vert} \right).
\end{equation}
Here, $\mu_{m,q}^u$ and $\mu_{n,q}^v$ are the $q^{\textrm{th}}$ nearest neighbors to the centroids $\mu_m^u$ and $\mu_n^v$, respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

>>>>

The similarity between the scene centroids $\mu_m^u$ over the entire dataset, is computed using a radial basis function (RBF) kernel $K$ combined with a local scaling method~\cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{mn}^{uv} = \exp\left( - \dfrac{\Vert \mu_m^u - \mu_n^v \Vert^2}{\Vert \mu_m^u - \mu_{m,q}^u \Vert \Vert \mu_n^v - \mu_{n,q}^v \Vert} \right).
\end{equation}
Here, $\mu_{m,q}^u$ and $\mu_{n,q}^v$ are the $q^{\textrm{th}}$ nearest neighbors to the centroids $\mu_m^u$ and $\mu_n^v$, respectively, and the double bars $\Vert \cdot \Vert$ denotes the Euclidean norm.
